The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-15 paper/mri_paper.tex
beginning of appendix

\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{color}

@@

Our domain is designed to be relevant to the design of the Princeton Plasma Physics Laboratory (PPPL) MRI experiment. The experimental apparatus is tall, one of many attributes designed to mitigate the meridional flows introduced by the endcaps. We use periodic vertical boundary conditions. On the radial boundaries of our domain --  the inner and outer cylinders -- we apply no-slip, perfectly conducting boundary conditions.

@@

\beq
\mathbf{V}^\dagger = \mathbb{V}^\dagger e^{iQz} + c.c.
\eeq

The elimination of this inner product must also be enforced the terms in Equation \ref{ordere3} that are resonant with $e^{i k_c z}$, yielding

@@

@@

>>>>

\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{appendix}
\usepackage[titletoc,title]{appendix}

@@

Our domain is designed to be relevant to the design of the Princeton Plasma Physics Laboratory (PPPL) MRI experiment (\citei{Ji:2001kd}). The experimental apparatus is tall, one of many attributes designed to mitigate the meridional flows introduced by the endcaps. We use periodic vertical boundary conditions, so our set-up represents an idealized domain where endcap contamination does not exist. On the radial boundaries of our domain --  the inner and outer cylinders -- we apply no-slip, perfectly conducting boundary conditions.

@@

\beq
\mathbf{V}^\dagger = \mathbb{V}^\dagger(x) e^{iQz} + c.c.
\eeq

where, again, $\mathbb{V}^\dagger$ contains the radial contribution. The elimination of this inner product must also be enforced the terms in Equation \ref{ordere3} that are resonant with $e^{i k_c z}$, yielding

@@

\newpage
\begin{appendices}
\begin{widetext}
\section*{Appendix A.}
\begin{multline}
N_{31}^{(A)} = -i Q \left(A_{11}\cdot\partial_x \Psi_{20}\right) - i Q \left(A_{11} \cdot \partial_x \Psi_{20}^*\right)
 + i Q \left(A_{11}^* \cdot \partial_x \Psi_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot \Psi_{22}\right) \\
 + i Q \left(\Psi_{11} \cdot \partial_x A_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x A_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x A_{22} \right) - i 2 Q \left(\partial_x \Psi_{11}^* \cdot A_{22}\right)
\end{multline}

\end{widetext}
\end{appendices}

@@

\bibitem[{Ji et al.(2001)}]{Ji:2001kd}
Ji, H, Goodman, J, Kageyama, A, Mon. Not. R. Astron. Soc., 325, 1
